Characterizing subarctic European vegetation's response on key environmental variables for land surface modeling of ozone pollution and risk assessment

### 2021-10-04 VegOzone.tex
Remove comment on uploade to zenodo

\dataavailability{All data is available from public databases or through institutional access. $\mathrm{DO_3SE}$ modeling results can be made available upon request {\bf TODO: Upload to an achieve together with processed, gap filled input data on zenodo?}.} %% use this section when having only data sets available

>>>>

\dataavailability{All data is available from public databases or through institutional access. $\mathrm{DO_3SE}$ modeling results can be made available upon request.} %% use this section when having only data sets available
